### 2013-05-06 doc/dissertation/document/chapters/mc_background/mc_background.tex
starting reduced domain approximation in mc background

\begin{figure}[p!]
  \centering
  \includegraphics[width=5in,clip]{chapters/mc_background/absorption_time.pdf}
  \caption{\textbf{CPU Time (s) to converge vs. artificial absorption
      probability for a $200 \times 200$ square mesh and 40,000
      histories.}  \textit{The reduced random walk length speeds up
      the calculation with a fixed number of histories. Too much
      artificial absorption increases iterations rapidly giving an
      increasing CPU time.}}
  \label{fig:absorption_time}
\end{figure}

\subsection{Reduced Domain Approximation}
\label{subsec:reduced_domain_approximation}

>>>>

\begin{figure}[p!]
  \centering
  \includegraphics[width=5in,clip]{chapters/mc_background/absorption_time.pdf}
  \caption{\textbf{CPU Time (s) to converge vs. artificial absorption
      probability for a $200 \times 200$ square mesh and 40,000
      histories.}  \textit{The reduced random walk length speeds up
      the calculation with a fixed number of histories. Too much
      artificial absorption increases iterations rapidly giving an
      increasing CPU time.}}
  \label{fig:absorption_time}
\end{figure}
\clearpage

\subsection{Reduced Domain Approximation}
\label{subsec:reduced_domain_approximation}
For scalable parallel implementations and efficient Monte Carlo
transport, the domain is required to be sparse. We may find through
general preconditioning operations as outlined by the Monte Carlo
problem in Eq~(\ref{eq:left_right_correction}) that this sparsity is
lost. To alleviate this, we propose modifying the domain sampled by
the Monte Carlo method to generate the correction within MCSA by
removing terms in the iteration matrix through some predetermined
criteria in order to recover sparsity. As the Neumann-Ulam scheme is a
stochastic realization of multiple matrix-vector multiplies, the
criteria we choose should be based on maintain those elements that
will make the largest contributions to the multiplication. For each
row in the preconditioned system, we can then apply the reduced domain
approximation to eliminate those elements that either fall below a
specified tolerance level, keep the $N$ largest elements in a row, or
both giving:
\begin{subequations}
  \begin{gather}
    \ve{x}^{k+1/2} = \ve{x}^k + \ve{r}^k\:,\\
    \ve{r}^{k+1/2} = \ve{b} - \ve{A}\ve{x}^{k+1/2}\:,\\
    \hat{\ve{A}}\delta\ve{x}^{k+1/2} = \ve{r}^{k+1/2}\:, 
    \label{eq:rda_correction}\\
    \ve{x}^{k+1} = \ve{x}^{k+1/2} + \delta \ve{x}^{k+1/2}\:,\\
    \ve{r}^{k+1} = \ve{b} - \ve{A}\ve{x}^{k+1}\:,
  \end{gather}
  \label{eq:rda_mcsa}
\end{subequations}
where $\hat{\ve{A}}$ in Eq~(\ref{eq:rda_correction}) means that the
reduced domain approximation has been applied to the iteration matrix
in the Monte Carlo method. If enough of the terms in the original
iteration matrix have been maintained, the character of the original
iteration matrix should be retained and continue to accelerate the
iterative scheme.
